Wireframe2DOM: From Static Graph to Responsive HTML

### 2020-05-02 document/paper.tex

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{llncs}
%
\usepackage{graphicx}
\usepackage{wrapfig}

% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}

@@

\section{Illustrative example}
% Shangyin
\section{Formal problem definition}
% Shangyin
In program synthesis setting, 
\section{Preliminaries}
% Shangyin
\subsection{Workflow}
\begin{wrapfigure}{r}{0.25\textwidth}
  \vspace*{-0.5in}
  \includegraphics[width=0.25\textwidth]{src/workflow.JPG}
\end{wrapfigure}
We define our workflow as a two-staged program. In the first stage, we synthesize the input Wireframe rectangles to IR. Then IR is compiled into universal HTML compatible with any browser in the second stage.

\subsection{IR Definition}

>>>>

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{llncs}
%
\usepackage{graphicx}
\usepackage{float}
\usepackage{wrapfig}

% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}
\usepackage{color, colortbl}
\definecolor{navy}{RGB}{0,0,205}
\definecolor{darkred}{RGB}{178,34,34}
\definecolor{darkblue}{RGB}{0,10,230}
\definecolor{green}{RGB}{20,180,20}
\definecolor{verylightgray}{RGB}{220,220,220}

% colors fo rules
\definecolor{darkgreen}{RGB}{0,153,0}
\definecolor{darkorange}{RGB}{204,102,0}

\newcommand{\dollar}{\mbox{\textdollar}}
\definecolor{campusgold}{RGB}{194,142,14}
\definecolor{headlinegold}{RGB}{152, 112, 13}
\definecolor{coalgray}{RGB}{77,64,56}
\definecolor{moongray}{RGB}{186,168,146}
\definecolor{everblue}{RGB}{91,104,112}
\definecolor{slayterblue}{RGB}{124,166,192}
\definecolor{ameliablue}{RGB}{163,214,215}
\definecolor{landgreen}{RGB}{8,92,17}
\definecolor{rossgreen}{RGB}{132,158,42}
\definecolor{celerygreen}{RGB}{195,190,11}
\definecolor{springgreen}{RGB}{233,228,91}
\definecolor{oakenbrown}{RGB}{107,69,52}
\definecolor{bellbrick}{RGB}{199,108,20}
\definecolor{mackeyorange}{RGB}{255,155,26}
\definecolor{yellowwalk}{RGB}{255,209,0}
\definecolor{fountainteal}{RGB}{46,175,155}
\definecolor{pappyspurple}{RGB}{173,31,101}

\usepackage[round]{natbib}
\usepackage{amsmath}
\usepackage{stmaryrd}
\usepackage{amsfonts}
\usepackage{listings}
\lstdefinelanguage{Scala}%
{morekeywords={abstract,%
  case,catch,char,class,%
  def,else,extends,final,finally,for,%
  if,import,implicit,%
  match,module,%
  new,null,%
  object,override,%
  package,private,protected,public,%
  for,public,return,super,%
  this,%throw,throws,
  trait,try,type,throw,%
  val,var,%
  with,while,%
  yield,%
  },%
  sensitive,%
  morecomment=[l]//,%
  morecomment=[s]{/*}{*/},%
  morestring=[b]",%
  morestring=[b]',%
  showstringspaces=false%
  inputencoding=utf8,
  extendedchars=true,
  moredelim=[is][\overbar]{`}{`},
  moredelim=[is][\sout]{~}{~},
  escapechar=@
}[keywords,comments,strings]%

\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{mauve}{rgb}{0.58,0,0.82}
\definecolor{violet}{rgb}{0.53, 0.0, 0.69}
\definecolor{violet2}{rgb}{0.93, 0.51, 0.93}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}

\lstset{
  language=Scala,
  basicstyle=\ttfamily,
  keywordstyle={\bfseries\color{violet}},
  commentstyle=\color{dkgreen},
  stringstyle=\color{blue},
  mathescape
}
\usepackage[T1]{fontenc}
\usepackage[scaled=0.9]{beramono}

@@

\section{Illustrative example}
% Shangyin
\section{Formal problem definition}
% Shangyin
In this work, we are given a list $L$, consisting of rectangles given their absolute coordinate with respective to origin. In addition, user provides the default size of the layout. All rectangles should be bounded by default size. Our objective is to find an equivalent HTML script which is: 
\begin{enumerate}
  \item \textbf{Precise -} Render the exact same layout when opened in  default size.
  \item \textbf{Responsive -} Automatically adjust the elements rendering if the browser is resized.
\end{enumerate}
\section{Preliminaries}
% Shangyin
\subsection{Workflow}
\begin{figure}[H]
  \vspace*{-0.1in}
  \includegraphics[width=1\textwidth]{src/workflow.JPG}
  \caption{Workflow}
\end{figure}
We define our workflow as a two-staged program. In the first stage, we synthesize the input Wireframe rectangles to IR. Then IR is compiled into universal HTML compatible with any browser in the second stage. 
\subsection{Input}
The input is defined as a list of rectangles, given their coordinates related to $(0,0)$, the upper-left corner of the canvas. For the consistency, we record the coordinates of the upper-left corner of a rectangle, as well as its width and height.
\subsection{IR Definition}
As discussed before, the intermediate presentation captures the nested hierarchy of raw rectangles. To maintain the hierarchical structure, we defined the data structure below.
\begin{figure}[H]
\vspace*{-0.2in}
\begin{lstlisting}[language=Scala,mathescape=true]
size = <Int, Int>
Div = <size>
HDiv = <size, VDiv*, Grid*, Div*>
VDiv = <size, HDiv*, Grid*, Div*>
Grid = <size, VDiv*, HDiv*, Div*>
Layout = Div | Grid | VDiv | HDiv
\end{lstlisting}
\caption{Definition of IR}
\end{figure}
We define \lstinline|Div| to be basic component of the hierarchy, which is equivalent to a raw rectangle in the input. All solid input rectangles are transformed into \lstinline|Div|s in different level of the tree in separate time during synthesizing. The three virtual containers for hierarchy are   \lstinline|HDiv|, \lstinline|VDiv|, \lstinline|GDiv|. As the name suggests, child containers of \lstinline|HDiv| and \lstinline|VDiv| are rendered in horizontal and vertical direction respectively. We define \lstinline|Grid| to behave like an HTML grid: two-dimensional container with auto row-wrapping. It contains homogenous elements, all rendered with same margin.
